A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Internal signatures

% XXX, esp. pullback

Given an internal signature~$\Sigma$ internal to a Grothendieck topos~$\E$ (or
elementary topos with a natural numbers object), we can successively build the
object of contexts (the object of lists of sorts); the object of terms
(equipped with a morphism to the object of contexts); the object of atomic
propositions (again equipped with such a morphism); the object of geometric
formulas (again so); the object of geometric sequents (again so); and, given an
internal geometric theory~$\TT$ over~$\Sigma$, the object of proof trees of~$\TT$.

@@

Disjunctions appearing in internal geometric formulas may be indexed by
arbitrary objects of the topos, just like disjunctions appearing in ordinary
external geometric formulas over an ordinary signature may be indexed by
arbitrary sets. If~$\E$ is a Grothendieck topos, the object of geometric
formulas over an internal signature~$\Sigma$ in~$\E$ has an important
subobject, the subobject of those formulas such that locally, any appearing
disjunction is indexed by a constant sheaf. Such internal geometric formulas
will be called \emph{geometric$^\star$ formulas}.

>>>>

The notions of signatures, geometric theories and classifying toposes can be
relativized to the internal world of arbitrary toposes with natural numbers
objects. Basics on internal signatures, internal geometric
theories and internal classifying toposes are
folklore~\cite[p.~334]{wraith:intuitionistic-algebra}; a careful treatment is
due to Shawn Henry~\cite{henry:phd}.

Briefly, an internal signature~$\Sigma$ internal to a topos~$\E$ consists of an
object of sorts, an object of function symbols, an object of relation symbols,
and various morphisms indicating the sorts involved with the function and
relation symbols.

Given an internal signature~$\Sigma$ internal to a Grothendieck topos~$\E$ (or
elementary topos with a natural numbers object), we can successively build the
object of contexts (the object of lists of sorts); the object of terms
(equipped with a morphism to the object of contexts); the object of atomic
propositions (again equipped with such a morphism); the object of geometric
formulas (again so); the object of geometric sequents (again so). A internal
geometric theory~$\TT$ over~$\Sigma$ is then given by a subobject of the object
of geometric sequents, interpreted as the object of axioms of~$\TT$. Given such
an internal theory~$\TT$, we can build the object of proof trees of~$\TT$.

@@

\begin{ex}An ordinary geometric theory~$\TT$ over an ordinary
signature~$\Sigma$ can be pulled back along a geometric morphism~$\E \to \Set$
to yield an internal geometric theory~$\ul{\TT}$ over the internal
signature~$\ul{\Sigma}$ in~$\E$. The object of sorts of~$\ul{\Sigma}$ is the pullback of
the set of sorts of~$\Sigma$, and so on.\end{ex}

Disjunctions appearing in internal geometric formulas may be indexed by
arbitrary objects of the topos, just like disjunctions appearing in ordinary
external geometric formulas over an ordinary signature may be indexed by
arbitrary sets. If~$\Sigma$ is an internal signature in a Grothendieck topos~$\E$, the object of geometric
formulas over~$\Sigma$ has an important
subobject, the subobject of those formulas such that locally, any appearing
disjunction is indexed by a constant sheaf. Such internal geometric formulas
will be called \emph{geometric$^\star$ formulas}.
